### 2020-02-28 Thesis-Chapter2-Background.tex
Improve file naming scheme, work on background

\chapter{Background}

@@

\section{Exceptional Access: Arguments For and Against}

@@

Primary reasons (why EA itself is beneficial):
\begin{itemize}
    \item Absolute privacy is not a right
    \item Encryption gives too much power to the individual
    \item EA would allow more crimes to be prevented and prosecuted
\end{itemize}

Secondary reasons (why studying EA is beneficial):
\begin{itemize}
    \item EA done well would be more secure and privacy preserving than EA done poorly
    \item The threat of legislative action creates urgency
\end{itemize}

@@

Primary reasons (why EA itself is bad):
\begin{itemize}
    \item Privacy is an absolute right
    \item Exceptional access gives too much power to the state
    \item Exceptional access is not possible in an acceptably secure manner
\end{itemize}

Secondary reasons (why studying EA is non-beneficial):
\begin{itemize}
    \item With both security and privacy in a poor state, research should be focused on strengthening, not weakening,
            them
    \item The technical community should not entertain delusions about what is truly possible
\end{itemize}

>>>>

\chapter{Background}
\label{chap-background}

@@

\section{Exceptional Access: Arguments For and Against}
\label{sec-argsbackground}

The debate over exceptional access takes place on two fundamental levels:
\begin{enumerate}
    \item Whether cryptosystems with exceptional access represent a net benefit to society
    \item Whether and how to conduct exceptional access research
\end{enumerate}

These arguments are introduced here and analyzed in detail in Chapter \ref{chap-arguments}.

@@

Why EA is a benefit to society:
\begin{itemize}
    \item Absolute privacy is not a right
    \item Encryption gives too much power to the individual
    \item EA would allow more crimes to be prevented and prosecuted
\end{itemize}

Why to research EA:
\begin{itemize}
    \item EA done well would be more secure and privacy preserving than EA done poorly
    \item The threat of legislative action creates urgency
\end{itemize}

@@

Why EA is a danger to society:
\begin{itemize}
    \item Privacy is an absolute right
    \item Exceptional access gives too much power to the state
    \item Exceptional access is not possible in an acceptably secure manner
\end{itemize}

Why not to research EA:
\begin{itemize}
    \item With both security and privacy in a poor state, research should be focused on strengthening, not weakening,
            them
    \item The technical community should not entertain delusions about what is truly possible
\end{itemize}
